### 2020-03-09 README.Rmd
Also wrote predict_bayesian_model. For some reason I can get fit_bayesain_model to run in console but not in markdown document.

```{r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("rudeboybert/forestecology")
```

@@

```{r}
bw_fit_model <- focal_vs_comp_bw %>% fit_bayesian_model(model_specs = bw_specs)
```

@@

>>>>

```{r, eval = FALSE}
# install.packages("remotes")
# remotes::install_github("rudeboybert/forestecology")
```

@@

```{r, eval = F}
bw_fit_model <- focal_vs_comp_bw %>% 
  fit_bayesian_model(model_specs = bw_specs)
```

@@

```{r, eval = F}
bw_predict <- focal_vs_comp_bw %>% 
  predict_bayesian_model(model_specs = bw_specs, posterior_param = bw_fit_model)

bw_predict %>%
  ggplot(aes(growth, growth_hat)) +
  geom_point() +
  stat_smooth(method = 'lm') +
  geom_abline(slope = 1, intercept = 0)
```
